Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-08 manuscript.tex
Update on Overleaf.

However, it was not until the study of the interaural time difference (ITD) by Gerstner in 1996~\citep{gerstner_neuronal_1996} that it was discovered that this delay is not homogeneous for all neurons of the same type and species, but adapts according to their function. This ITD is a biological mechanism which allows for the azimutal localization of sound by barn owls, by organically computing the difference in arrival time of a sound between their two ears. According to Gerstner, there is a true paradox in auditory neural systems since “neural networks encode behaviourally relevant signals in the range of a few $\mu s$ with neurons that are at least one order of magnitude slower”, therefore necessarily need to play on the response time to do so. \citet{pena_2001} conducted an extended study on ITD in order to confirm this theory by identifying the coincidence detector involved, which the authors situated in the nuclear laminaris. A first hypothesis suggested that the sound coincidence was detected using stereausis, i.e. the temporal disparity between left and right cochlear loci in the owl's brain. However it was quickly set aside as the predictions did not match the measured disparities in the loci, and no variations were perceived in the nuclear laminaris for a similar sound intensity in both owl ears. The authors support a second hypothesis, that of different axonal delays in the ipsi and contralateral cochlear nucleus magnocellularis. \citet{seidl_mechanisms_2010} experimentally seconds this hypothesis of a "coarse" regulation of delay, as the authors conclude that regulations at different sites within individual axons of at least two parameters, namely the axon diameter and internode distances, might be responsible for precise adjustments of physiological delays thus allowing the ITD detection. These experiments also confirmed previous studies stating that the conduction velocity of a spike in a neuron (in other words, its delay) depends strongly on the axon diameter \cite{gasser_1939} and the internode distance between Ranvier nodes \cite{brills_1977} --- instead of the axon's length as was previously stated \cite{??}.

@@

\cite{gasser_1939} experimentally confirmed with homogeneously selected neurons that the axonal delay is positively proportional to the axon diameter, i.e. the amount of myelin wrapped around the axon. Indeed, the oligodendrocytes, one of the many glial cells present in the Vertebrates' nervous system, wrap \cite{???}

>>>>

However, it was not until the study of the interaural time difference (ITD) by Gerstner in 1996~\citep{gerstner_neuronal_1996} that it was discovered that this delay is not homogeneous for all neurons of the same type and species, but adapts according to their function. This ITD is a biological mechanism which allows for the azimutal localization of sound by barn owls, by organically computing the difference in arrival time of a sound between their two ears. According to Gerstner, there is a true paradox in auditory neural systems since “neural networks encode behaviourally relevant signals in the range of a few $\mu s$ with neurons that are at least one order of magnitude slower”, therefore necessarily need to play on the response time to do so. \citet{pena_2001} conducted an extended study on ITD in order to confirm this theory by identifying the coincidence detector involved, which the authors situated in the nuclear laminaris. A first hypothesis suggested that the sound coincidence was detected using stereausis, i.e. the temporal disparity between left and right cochlear loci in the owl's brain. However it was quickly set aside as the predictions did not match the measured disparities in the loci, and no variations were perceived in the nuclear laminaris for a similar sound intensity in both owl ears. The authors support a second hypothesis, that of different axonal delays in the ipsi and contralateral cochlear nucleus magnocellularis. \citet{seidl_mechanisms_2010} experimentally seconds this hypothesis of a "coarse" regulation of delay, as the authors conclude that regulations at different sites within individual axons of at least two parameters, namely the axon diameter and internode distances, might be responsible for precise adjustments of physiological delays thus allowing the ITD detection. These experiments also confirmed previous studies stating that the conduction velocity of a spike in a neuron (in other words, its delay) depends strongly on the axon diameter \cite{gasser_1939} and the internode distance between Ranvier nodes \cite{brills_1977} --- instead of the axon's length as was previously thought \cite{??}.

@@

\cite{gasser_1939} experimentally confirmed with homogeneously selected neurons that the axonal delay is positively proportional to the axon diameter, i.e. the amount of myelin wrapped around the axon. Indeed, the oligodendrocytes, one of the many glial cells present in the Vertebrates' nervous system, produce  \cite{???}
